Space astrometry of the very massive $\sim$$150\,M_\odot$ candidate runaway star VFTS682

### 2018-09-28 MNRASformat/VFTS682_MNRASL.tex
added vink book ref

 \hline     
      \multicolumn{5}{l}{\emph{HST proper motion of VFTS682 relative
      to R136}} \\
            \hline
      &$\delta\mu_\mathrm{RA, HST}$  &[$\masyr$] & $0.02\pm0.10$ & (5) \\
      &$\delta\mu_\mathrm{DEC, HST}$  &[$\masyr$] & $0.19\pm0.09$ &  (5) \\
       &$\delta\mu_\mathrm{HST}$  &[$\masyr$] & $0.19\pm0.09$ &  (5) \\
                  &$v_\mathrm{2D, HST}$  &[$\kms$] & $45\pm21$ & (5)\\  
                      &$\theta_\mathrm{HST}$  &[degrees] &   $-30_{-51}^{+24}$   & (1,6)\\  
                  %        &$v_\mathrm{2D, \parallel}$  &[$\kms$] & $\SdM{xxx}\pm\SdM{xxx}$ & (1,5)\\  
      \hline
      \multicolumn{5}{l}{\emph{Weighted average relative proper motion
      for VFTS682}}\\
      \hline
      &$\delta\mu_\mathrm{RA, avg}$  &[$\masyr$] & $0.08\pm0.07$ & (6) \\
      &$\delta\mu_\mathrm{DEC, avg}$  &[$\masyr$] & $0.14\pm0.07$ &  (6) \\
       &$\delta\mu_\mathrm{avg}$  &[$\masyr$] & $0.16\pm0.07$ &  (6) \\
      &$v_\mathrm{2D, avg}$  &[$\kms$] & $38\pm17$ & (6)\\
      % &$\theta_\mathrm{avg}$  &[degrees] &  \todo{TBD} $_{-}^{+}$   & (5)\\  
      \hline
       \multicolumn{5}{l}{\emph{Expected proper motion if ejected from
      R136 at age zero}} \\
      \hline
      &$v_\mathrm{2D}$  &[$\kms$] & $29\pm 6$ & (3) \\  
      &$\theta$  &[degrees] &  $\sim0$  & \\ 
       \hline
    \end{tabular}
    {\tiny The error on the RA and DEC positions, are of order
      $\sim$$0.01\masyr$ in \emph{Gaia}
      DR2. Assuming a distance of 50\,kpc, $1\masyr$ corresponds to $237\kms$.
$\rho(\mu_\mathrm{RA},\mu_\mathrm{DEC})$ is the
      correlation coefficient. The position angle
      $\theta$ is defined such that $\theta=0$ for radial motion
      away from R136. We neglect the error bars on
      $\langle\mu_\mathrm{RA}\rangle_\mathrm{R136}$ and $\langle\mu_\mathrm{DEC}\rangle_\mathrm{R136}$ to determine the uncertainty
      on $\theta_{Gaia}$.
      (1)~\cite{brown:18},
      (2)~\cite{henault-brunet:12},
      (3)~\cite{bestenlehner:11},
      (4)~\cite{lennon:18}, 
      (5)~\cite{platais:18} and
      (6)~{\color{blue}this study}.
    }
  \end{center}
  \label{tab:vfts682}
\end{table}

The WNh5 star VFTS682, located at right ascension (RA)
05$^\mathrm{h}$38$^\mathrm{m}$55.510$^\mathrm{s}$  and declination
(DEC) \mbox{-69$^\mathrm{o}$04'26.72''} (J2000), was observed as part of the multi-epoch, spectroscopic VFTS campaign covering $\lambda$4000--7000 \citep[][]{evans:11}. 
\citet{bestenlehner:11}  analyzed the spectra to infer the stellar
parameters and measured a \newtext{visual} extinction of $A_V=4.45\pm0.12$, implying a
luminosity of $\log_{10}(L/L_\odot) =  6.5\pm0.2$, making this one of
the most luminous stars in the region. The absence of periodic radial
velocity (RV)
variations suggests that the star is unlikely to have close
companions \citep[][]{bestenlehner:11}, unless the orbital inclination is
very high. Bayesian fits of the stellar
parameters against evolutionary tracks \citep{brott:11, kohler:15}
using the BONNSAI code \citep{schneider:14,schneider:17} provide
estimates for the age, present mass and initial mass, % indicating that
% this star among the most massive stars known,
see
% as given in 
\Tabref{tab:star_param}. % for an overview of the parameters.

@@

\begin{figure}%[tbp]
  \centering
  \includegraphics[width=0.35\textwidth]{figures/dist_mu_region.pdf}\\
  \vspace*{-5pt}
  \includegraphics[width=0.35\textwidth]{figures/angle}
  % \caption{\emph{Top panel}: distribution of OB-type and Wolf-Rayet stars in proper
  %   motion relative to R136 from \emph{Gaia} DR2. VFTS682 is not an outlier, but
  %   its relative proper motion matches the expected value (green
  %   vertical band) if it were indeed
  %   ejected from R136 assuming an age of $1.0\pm0.2$\,Myr. %The top axis shows the conversion to $\kms$
  %   % assuming a distance of 50\,kpc.
  %   \emph{Bottom panel}:  distribution of
  %   angles between the relative proper motion direction and the radial
  %   direction from the center of the cluster to the star. The error bars from \emph{Gaia} for VFTS682 are large, but
  %   the best value is in agreement with the hypothesis of dynamical
  %   ejection (green vertical band). The peak at $\theta\simeq\pi/2$ is due to stars
  %   belonging to NGC2060. In both
  %   panels, the dark blue histograms contain 317 
  %   stars with error bars smaller than $0.1\,\mathrm{mas \
  %     yr^{-1}}\simeq25\,\mathrm{km\ s^{-1}}$ at 50\,kpc, the
  %   lighter blue histograms contain 36 stars with error bars smaller than $0.05\,\mathrm{mas \
  %   yr^{-1}}$. }
  \vspace{-5pt}
  \caption{Distribution of OB-type and Wolf-Rayet stars in proper
    motion relative to R136 (top panel) and proper motion position angle
    (bottom panel), from \emph{Gaia} DR2. Although VFTS682 is not an outlier, its relative
    proper motion matches the value expected for an early dynamical
    ejection \newtext{(see \Secref{sec:results})}. In both
    panels, the dark blue histograms contain 317 
    stars with error bars smaller than $0.1\,\mathrm{mas \
      yr^{-1}}\simeq25\,\mathrm{km\ s^{-1}}$ at 50\,kpc and the
    lighter blue histograms contain 36 stars with error bars smaller than $0.05\,\mathrm{mas \
    yr^{-1}}$. The peak at $\theta\simeq\pi/2$ in the bottom panel is due to stars
  belonging to NGC2060. }
\vspace{-10pt}
  \label{fig:dist}
\end{figure}

@@

\begin{figure}%[tbp]
  \centering
  \includegraphics[width=0.5\textwidth]{./figures/fig2}  
  \caption{The thick red arrow shows the proper motion
    relative to R136 for VFTS682 from averaging the \emph{Gaia} DR2 and HST
  astrometry, multiplied by 0.4\,Myr. The extension in the opposite
  direction is proportional to the apparent age of the star, and the
  thin lines illustrate the error cone on the potential origin. The
  yellow arrows show the \emph{Gaia} DR2 results alone, and the orange
  arrow the HST results alone. The two blue circles indicate the regions of radii 0.01 and 0.05
   degrees around the core of R136.}  
  \label{fig:main}
\end{figure}

\vspace*{-15pt}
\subsection{ \emph{Gaia} astrometry for VFTS682\label{data:gaia}}

@@

Figure~\ref{fig:main} shows the motion of VFTS682 relative to R136
projected on the
sky. We also show VFTS16 and VFTS72 %for completeness
\citep[see][]{lennon:18}. The thick yellow arrows are proportional to
the relative proper motion from \emph{Gaia} DR2, the thick green
line illustrates the relative proper motion from HST, and the thick
purple line shows the averaged result. The error cone
on the direction of motion is illustrated by the corresponding
extension in the direction opposite to the motion, and we also show
the most likely origin of the stars accounting for their apparent age
\newtext{($0.7\pm0.1$\,Myr and $0.4^{+0.8}_{-0.4}$\,Myr for VFTS16 and VFTS72,
respectively \citealt{schneider:18})}.
This figure illustrates that R136 is the most likely origin of these stars, although the large error bars
prevent a robust identification for VFTS682, and there is some tension
between the apparent age and the present day distance from the cluster
core for VFTS16 and VFTS72 \citep[][]{lennon:18}. We note that
VFTS72 has a small radial velocity, while VFTS16 (and possibly VFTS682) has
a large peculiar radial velocity, and therefore accurate distances along
the line of sight are
needed to constrain the flight direction in three dimensions.

@@

Also \cite{fujii:11} suggest that
early in the evolution of a cluster, dynamical interactions form an extremely
massive binary, which then tightens its orbit by ejecting other
stars. The spectral similarities between VFTS682 and stars in the core
of R136 are in agreement with this ``bully binary'' model. Interpreting the kinematics of VFTS682 through the lens of their simulations
suggests the presence of a close binary with total mass
$M_1+M_2\gtrsim 300\,M_\odot$ in the core of the cluster. The
\newtext{difference between the cluster age and the} kinematic age of VFTS682 puts an
upper limit to the timescale to form the ``bully binary'' in
R136 of \newtext{$\sim$$1.3\,\mathrm{Myr}$}. If identified, such a binary % could be R145 according to \cite{fujii:11}, and it
might be an ideal observational candidate for a dynamically formed progenitor system of
a binary black-hole, provided that stars this massive can avoid a
pair-instability supernova \cite[e.g.,][]{rakavy:67} at LMC
metallicity \citep[see also][]{langer:07, woosley:17}.
Similarly, the final fate of VFTS682 could be either a
pair-instability supernova without compact remnant formation, or
possibly direct collapse to a black hole. The amount of mass loss of these stars will determine their final core
mass and thus their final fate.

VFTS682 is potentially the most massive runaway known to date, and its ejection
from the cluster R136 likely implies that it is only the ``tip of the
iceberg'' of massive runaways in the
region. Studies of this population, enabled by recent and future %HST
% and \emph{Gaia}
observations will put constraints on the evolution
of these extreme stars, together with the formation and evolution of
the central cluster itself.
\vspace*{-40pt}
\bibliographystyle{mnras}
\bibliography{bibliography/vfts682}

@@

\vspace*{-25pt}
\section*{Affiliations}
 \tiny
\noindent $^{1}${Astronomical Institute Anton Pannekoek, University of
    Amsterdam, 1098 XH Amsterdam, The Netherlands} 
  $^{2}$ {ESA, European Space Astronomy Centre, Apdo. de Correos 78,
    E-28691 Villanueva de la Ca\~nada, Madrid, Spain} 
 $^{3}$ {Instituto de Astrof\'isica de Canarias, E-38205 La Laguna, Tenerife, Spain}
 %Center for Astrophysical Sciences, 
$^4$ {Department of Physics \& Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}
  $^{5}$ {Space Telescope Science Institute, 3700 San Martin Drive,
    Baltimore, MD 21218, USA}
  $^{6}${Department of Physics and Astronomy, Hicks Building,
    Hounsfield Road, University of Sheffield, Sheffield S3 7RH, UK}
  $^{7}${UK Astronomy Technology Centre, Royal Observatory Edinburgh, Blackford Hill, Edinburgh, EH9 3HJ, UK}
  $^{8}$ {National Research Council, Herzberg Astronomy \&
    Astrophysics, 5071 West Saanich Road, Victoria, BC, V9E 2E7,
    Canada}
  $^{9}$ {School of Astronomy \& Space Science, University of the Chinese
    Academy of Sciences, Beijing 100012, China}
  $^{10}$ {National Astronomical Observatories, Chinese Academy of
    Sciences, Beijing 100012, China}
  $^{11}$ {Argelander-Instit\"ut f\"ur Astronomie, Universit\"at Bonn,
    Auf dem H\"ugel 71, 53121, Bonn, Germany}
  $^{12}$ {Centro de Astrobiolog\'ia, CSIC-INTA, Carretera de Torrej\'on a Ajalvir km-4, E-28850 Torrej\'on de Ardoz, Madrid, Spain}
  $^{13}$ {Institute of Astronomy, KU Leuven, Celestijnenlaan 200 D, B-3001 Leuven, Belgium}
  $^{14}$ {Department of Physics, University of Oxford, Keble Road,
    Oxford OX13RH, UK} 
  $^{15}$ {Armagh Observatory, College Hill, Armagh BT619DG, UK}

  % \begin{acknowledgements}
  {   \tiny
    We thank P.~Crowther, J.~Heyl, M.\,C.\,Ramirez-Tannus, S.~N.~Shore,
    and S.\,Torres, and the HSTPROMO Collaboration
    for help and discussions. SdM acknowledges
    the European Unions Horizon 2020 research and innovation programme
    from the European Research Council (ERC), Grant agreement No. 715063
    and VHB the NRC-Canada Plaskett Fellowship. This study has used data from the ESA mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
  }
% \end{acknowledgements}

>>>>

 \hline     
      \multicolumn{5}{l}{\emph{HST proper motion of VFTS682 relative
      to R136}} \\
            \hline
      &$\delta\mu_\mathrm{RA, HST}$  &[$\masyr$] & $0.02\pm0.10$ & (5) \\
      &$\delta\mu_\mathrm{DEC, HST}$  &[$\masyr$] & $0.19\pm0.09$ &  (5) \\
       &$\delta\mu_\mathrm{HST}$  &[$\masyr$] & $0.19\pm0.09$ &  (5) \\
                  &$v_\mathrm{2D, HST}$  &[$\kms$] & $45\pm21$ & (5)\\  
                      &$\theta_\mathrm{HST}$  &[degrees] &   $-30_{-51}^{+24}$   & (1,6)\\  
                  %        &$v_\mathrm{2D, \parallel}$  &[$\kms$] & $\SdM{xxx}\pm\SdM{xxx}$ & (1,5)\\  
      \hline
      \multicolumn{5}{l}{\emph{Weighted average relative proper motion
      for VFTS682}}\\
      \hline
      &$\delta\mu_\mathrm{RA, avg}$  &[$\masyr$] & $0.08\pm0.07$ & (6) \\
      &$\delta\mu_\mathrm{DEC, avg}$  &[$\masyr$] & $0.14\pm0.07$ &  (6) \\
       &$\delta\mu_\mathrm{avg}$  &[$\masyr$] & $0.16\pm0.07$ &  (6) \\
      &$v_\mathrm{2D, avg}$  &[$\kms$] & $38\pm17$ & (6)\\
      % &$\theta_\mathrm{avg}$  &[degrees] &  \todo{TBD} $_{-}^{+}$   & (5)\\  
      \hline
       \multicolumn{5}{l}{\emph{Expected proper motion if ejected from
      R136 at age zero}} \\
      \hline
      &$v_\mathrm{2D}$  &[$\kms$] & $29\pm 6$ & (3) \\  
      &$\theta$  &[degrees] &  $\sim0$  & \\ 
       \hline
    \end{tabular}
    {\tiny The error on the RA and DEC positions, are of order
      $\sim$$0.01\masyr$ in \emph{Gaia}
      DR2. Assuming a distance of 50\,kpc, $1\masyr$ corresponds to $237\kms$.
$\rho(\mu_\mathrm{RA},\mu_\mathrm{DEC})$ is the
      correlation coefficient. The position angle
      $\theta$ is defined such that $\theta=0$ for radial motion
      away from R136. We neglect the error bars on
      $\langle\mu_\mathrm{RA}\rangle_\mathrm{R136}$ and $\langle\mu_\mathrm{DEC}\rangle_\mathrm{R136}$ to determine the uncertainty
      on $\theta_{Gaia}$.
      (1)~\cite{brown:18},
      (2)~\cite{henault-brunet:12},
      (3)~\cite{bestenlehner:11},
      (4)~\cite{lennon:18}, 
      (5)~\cite{platais:18} and
      (6)~{\color{blue}this study}.
    }
  \end{center}
  \label{tab:vfts682}
\end{table}
The WNh5 star VFTS682, located at right ascension (RA)
05$^\mathrm{h}$38$^\mathrm{m}$55.510$^\mathrm{s}$  and declination
(DEC) \mbox{-69$^\mathrm{o}$04'26.72''} (J2000), was observed as part of the multi-epoch, spectroscopic VFTS campaign covering $\lambda$4000--7000 \citep[][]{evans:11}. 
\citet{bestenlehner:11}  analyzed the spectra to infer the stellar
parameters and measured a \newtext{visual} extinction of $A_V=4.45\pm0.12$, implying a
luminosity of $\log_{10}(L/L_\odot) =  6.5\pm0.2$, making this one of
the most luminous stars in the region. The absence of periodic radial
velocity (RV)
variations suggests that the star is unlikely to have close
companions \citep[][]{bestenlehner:11}, unless the orbital inclination is
very high. Bayesian fits of the stellar
parameters against evolutionary tracks \citep{brott:11, kohler:15}
using the BONNSAI code \citep{schneider:14,schneider:17} provide
estimates for the age, present mass and initial mass, % indicating that
% this star among the most massive stars known,
see
% as given in 
\Tabref{tab:star_param}. % for an overview of the parameters.

@@

\begin{figure}%[tbp]
  \centering
  \includegraphics[width=0.35\textwidth]{figures/dist_mu_region.pdf}\\
  \vspace*{-5pt}
  \includegraphics[width=0.35\textwidth]{figures/angle}
  % \caption{\emph{Top panel}: distribution of OB-type and Wolf-Rayet stars in proper
  %   motion relative to R136 from \emph{Gaia} DR2. VFTS682 is not an outlier, but
  %   its relative proper motion matches the expected value (green
  %   vertical band) if it were indeed
  %   ejected from R136 assuming an age of $1.0\pm0.2$\,Myr. %The top axis shows the conversion to $\kms$
  %   % assuming a distance of 50\,kpc.
  %   \emph{Bottom panel}:  distribution of
  %   angles between the relative proper motion direction and the radial
  %   direction from the center of the cluster to the star. The error bars from \emph{Gaia} for VFTS682 are large, but
  %   the best value is in agreement with the hypothesis of dynamical
  %   ejection (green vertical band). The peak at $\theta\simeq\pi/2$ is due to stars
  %   belonging to NGC2060. In both
  %   panels, the dark blue histograms contain 317 
  %   stars with error bars smaller than $0.1\,\mathrm{mas \
  %     yr^{-1}}\simeq25\,\mathrm{km\ s^{-1}}$ at 50\,kpc, the
  %   lighter blue histograms contain 36 stars with error bars smaller than $0.05\,\mathrm{mas \
  %   yr^{-1}}$. }
  \vspace{-5pt}
  \caption{Distribution of OB-type and Wolf-Rayet stars in proper
    motion relative to R136 (top panel) and proper motion position angle
    (bottom panel), from \emph{Gaia} DR2. Although VFTS682 is not an outlier, its relative
    proper motion matches the value expected for an early dynamical
    ejection \newtext{(see \Secref{sec:results})}. In both
    panels, the dark blue histograms contain 317 
    stars with error bars smaller than $0.1\,\mathrm{mas \
      yr^{-1}}\simeq25\,\mathrm{km\ s^{-1}}$ at 50\,kpc and the
    lighter blue histograms contain 36 stars with error bars smaller than $0.05\,\mathrm{mas \
    yr^{-1}}$. The peak at $\theta\simeq\pi/2$ in the bottom panel is due to stars
  belonging to NGC2060.}
\vspace{-5pt}
  \label{fig:dist}
\end{figure}

@@

\begin{figure}%[tbp]
  \centering
  \includegraphics[width=0.5\textwidth]{./figures/fig2}  
  \caption{The thick red arrow shows the proper motion
    relative to R136 for VFTS682 from averaging the \emph{Gaia} DR2 and HST
  astrometry, multiplied by 0.4\,Myr. The extension in the opposite
  direction is proportional to the apparent age of the star, and the
  thin lines illustrate the error cone on the potential origin. The
  yellow (orange) arrows show the \emph{Gaia} DR2 (HST) results alone. The two blue circles indicate the regions of radii 0.01 and 0.05
  degrees around the core of R136.}
\vspace{-5pt}
  \label{fig:main}
\end{figure}

\subsection{ \emph{Gaia} astrometry for VFTS682\label{data:gaia}}

@@

Figure~\ref{fig:main} shows the motion of VFTS682 relative to R136
projected on the
sky. We also show VFTS16 and VFTS72 %for completeness
\citep[see][]{lennon:18}. The yellow arrows are proportional to
the relative proper motion from \emph{Gaia} DR2, the orange
line illustrates the relative proper motion from HST, and the 
red arrow shows the averaged result. The error cone
on the direction of motion is illustrated by the corresponding
extension in the direction opposite to the motion, and we also show
the most likely origin of the stars accounting for their apparent age
\newtext{($0.7\pm0.1$\,Myr and $0.4^{+0.8}_{-0.4}$\,Myr for VFTS16 and VFTS72,
respectively \citealt{schneider:18})}.
This figure illustrates that R136 is the most likely origin of these stars, although the large error bars
prevent a robust identification for VFTS682, and there is some tension
between the apparent age and the present day distance from the cluster
core for VFTS16 and VFTS72 \citep[][]{lennon:18}. We note that
VFTS72 has a small radial velocity, while VFTS16 (and possibly VFTS682) has
a large peculiar radial velocity, and therefore accurate distances along
the line of sight are
needed to constrain the flight direction in three dimensions.

@@

Also \cite{fujii:11} suggest that
early in the evolution of a cluster, dynamical interactions form an extremely
massive binary, which then tightens its orbit by ejecting other
stars. The spectral similarities between VFTS682 and stars in the core
of R136 are in agreement with this ``bully binary'' model. Interpreting the kinematics of VFTS682 through the lens of their simulations
suggests the presence of a close binary with total mass
$M_1+M_2\gtrsim 300\,M_\odot$ in the core of the cluster. The
\newtext{difference between the cluster age and the} kinematic age of VFTS682 puts an
upper limit to the timescale to form the ``bully binary'' in
R136 of \newtext{$\sim$$1.3\,\mathrm{Myr}$}. % If identified, 
Such a binary % could be R145 according to \cite{fujii:11}, and it
might be a % an ideal observational
candidate for a dynamically formed progenitor system of
a binary black-hole, provided that stars this massive can avoid a
pair-instability supernova \cite[e.g.,][]{rakavy:67} at LMC
metallicity \citep[see also][]{langer:07, woosley:17}.
Similarly, the final fate of VFTS682 could be either a
pair-instability supernova without compact remnant formation, or collapse to a black hole. The amount of mass loss of these stars will determine their final core
mass and thus their final fate \newtext{\cite[e.g.,][]{vink:15}}.

VFTS682 is potentially the most massive runaway known to date, and its ejection
from the cluster R136 likely implies that it is only the ``tip of the
iceberg'' of massive runaways in the
region. Studies of this population, enabled by recent and future %HST
% and \emph{Gaia}
observations will put constraints on the evolution
of these stars, together with the formation and evolution of
the central cluster itself.
\vspace*{-30pt}
\bibliographystyle{mnras}
\bibliography{bibliography/vfts682}

@@

\vspace*{-25pt}
\section*{Affiliations and Acknowledgements}
 \tiny
\noindent $^{1}${Astronomical Institute Anton Pannekoek, University of
    Amsterdam, 1098 XH Amsterdam, The Netherlands} 
  $^{2}$ {ESA, European Space Astronomy Centre, Apdo. de Correos 78,
    E-28691 Villanueva de la Ca\~nada, Madrid, Spain} 
 $^{3}$ {Instituto de Astrof\'isica de Canarias, E-38205 La Laguna, Tenerife, Spain}
 %Center for Astrophysical Sciences, 
$^4$ {Department of Physics \& Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}
  $^{5}$ {Space Telescope Science Institute, 3700 San Martin Drive,
    Baltimore, MD 21218, USA}
  $^{6}${Department of Physics and Astronomy, Hicks Building,
    Hounsfield Road, University of Sheffield, Sheffield S3 7RH, UK}
  $^{7}${UK Astronomy Technology Centre, Royal Observatory Edinburgh, Blackford Hill, Edinburgh, EH9 3HJ, UK}
  $^{8}$ {National Research Council, Herzberg Astronomy \&
    Astrophysics, 5071 West Saanich Road, Victoria, BC, V9E 2E7,
    Canada}
  $^{9}$ {School of Astronomy \& Space Science, University of the Chinese
    Academy of Sciences, Beijing 100012, China}
  $^{10}$ {National Astronomical Observatories, Chinese Academy of
    Sciences, Beijing 100012, China}
  $^{11}$ {Argelander-Instit\"ut f\"ur Astronomie, Universit\"at Bonn,
    Auf dem H\"ugel 71, 53121, Bonn, Germany}
  $^{12}$ {Centro de Astrobiolog\'ia, CSIC-INTA, Carretera de Torrej\'on a Ajalvir km-4, E-28850 Torrej\'on de Ardoz, Madrid, Spain}
  $^{13}$ {Institute of Astronomy, KU Leuven, Celestijnenlaan 200 D, B-3001 Leuven, Belgium}
  $^{14}$ {Department of Physics, University of Oxford, Keble Road,
    Oxford OX13RH, UK} 
  $^{15}$ {Armagh Observatory, College Hill, Armagh BT619DG, UK}

  % \begin{acknowledgements}
  {   \tiny
    We thank P.~Crowther, J.~Heyl, M.\,C.\,Ramirez-Tannus, S.~N.~Shore,
    and S.\,Torres, and the HSTPROMO Collaboration
    for help and discussions. SdM acknowledges
    the European Unions Horizon 2020 research and innovation programme
    from the European Research Council (ERC), Grant agreement No. 715063
    and VHB the NRC-Canada Plaskett Fellowship. This study has used data from the ESA mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by % the {\it Gaia} Data Processing and Analysis Consortium (
    DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}.
  }
% \end{acknowledgements}
